---
title: "CREDIT_CARD_CASE_STUDY-shubhamjainxyz@gmail.com"
output: html_document
---

### IMPORTING DATASETS

```{r}
setwd("C:/Users/shubh/Desktop/Data Science Using R/Class 7 Data Science Using R")

customer_data <- read.csv("R Credit Card Case Study/Customer Acqusition.csv")
customer_data$No <- NULL
spend_data <- read.csv("R Credit Card Case Study/spend.csv")
spend_data$Sl.No. <- NULL
repay_data <- read.csv("R Credit Card Case Study/Repayment.csv")
repay_data$SL.No. <- NULL
```

### IMPORTING PACKAGES

```{r}
require(dplyr)
require(lubridate)
require(ggplot2)
require(plotly)
```

### RENAMING COLUMNS FOR BETTER UNDERSTANDING

```{r}
repay_data <- dplyr::rename(repay_data, "Amt_Repay" = "Amount") 
spend_data <- dplyr::rename(spend_data, "Amt_Spend" = "Amount")
```

### CONVERSION TO PROPER DATE FORMATS

```{r}
repay_data$Month <- lubridate::dmy(repay_data$Month)
spend_data$Month <- lubridate::dmy(spend_data$Month)
```

### Q1(a). REPLACE AGE WITH MEAN WHERE AGE IS LESS THAN 18

```{r}
customer_data[customer_data$Age < 18, "Age"]
customer_data[customer_data$Age < 18, "Age"] <- mean(customer_data$Age, na.rm = TRUE)
customer_data[customer_data$Age < 18, "Age"]
```

### Q1(b). IF AMT_SPEND > LIMIT REPLACE WITH 50% OF LIMIT

```{r}
customer_spend <- dplyr::left_join(x = customer_data, y = spend_data, by = c("Customer" = "Customer") ) 
head(customer_spend, 5)

head(customer_spend[customer_spend$Amt_Spend > customer_spend$Limit, "Amt_Spend"], 5)

customer_spend[customer_spend$Amt_Spend > customer_spend$Limit, "Amt_Spend"] <-  
0.5*customer_spend[customer_spend$Amt_Spend > customer_spend$Limit ,"Limit"]

head(customer_spend[customer_spend$Amt_Spend > customer_spend$Limit, "Amt_Spend"], 5)
```

### Q1(c). IF AMT_REPAY > LIMIT REPLACE WITH LIMIT.

```{r}
customer_repay <- dplyr::left_join(x = customer_data, y = repay_data, by = c("Customer" = "Customer"))
head(customer_repay, 5)

head(customer_repay[customer_repay$Amt_Repay > customer_repay$Limit, "Amt_Repay"], 5)

customer_repay[customer_repay$Amt_Repay > customer_repay$Limit, "Amt_Repay"] <-  
customer_repay[customer_repay$Amt_Repay > customer_repay$Limit ,"Limit"]

head(customer_repay[customer_repay$Amt_Repay > customer_repay$Limit, "Amt_Repay"], 5)
```

### Q2(a). NUMBER OF DISTINCT CUSTOMERS.

```{r}
distinct_customers <- count(dplyr::distinct(customer_data))
print(paste("No. of distinct customers is", distinct_customers ))
```

### Q2(b). NUMBER OF DISTINCT CATEGORIES(SEGMENTS).

```{r}
count_categories <- count(dplyr::distinct(customer_data, Segment))
print(paste("No. of distinct categories is", count_categories ))
```

### Q2(c). AVERAGE MONTHLY SPEND BY CUSTOMERS.

```{r}
avg_spend_mth <- customer_spend%>% dplyr::group_by(lubridate::year(Month))%>%dplyr::summarise(AVG_SPEND = sum(Amt_Spend)/12)
avg_spend_mth <- sum(avg_spend_mth$AVG_SPEND)/3
print(paste("Average Monthly Spend By All customers in a month is ", avg_spend_mth))
```

### Q2(d). AVERAGE MONTHLY REPAYMENT BY CUSTOMERS.

```{r}
avg_repay_mth <- customer_repay%>%dplyr::group_by(lubridate::year(Month))%>%dplyr::summarise(AVG_REPAY = sum(Amt_Repay)/12)
avg_repay_mth <- sum(avg_repay_mth)/3
print(paste("Average Monthly Repayment By All Customers in a month is ", avg_repay_mth))
```

### Q2(e). PROFIT FOR BANK FOR EACH MONTH.

```{r}
monthly_spend <- customer_spend %>% 
                 dplyr::group_by(lubridate::year(Month), lubridate::month(Month)) %>%
                 summarise(Amt_Spend = sum(Amt_Spend))

monthly_spend <- dplyr::rename(monthly_spend, "Year" = "lubridate::year(Month)",
                                              "Month" = "lubridate::month(Month)")

monthly_repay <- customer_repay %>% 
                 dplyr::group_by(lubridate::year(Month), lubridate::month(Month)) %>%
                 summarise(Amt_Repay = sum(Amt_Repay))
monthly_repay <- dplyr::rename(monthly_repay, "Year" = "lubridate::year(Month)",
                                              "Month" = "lubridate::month(Month)")

monthly_profit <- left_join(monthly_repay, monthly_spend, by = c("Year" = "Year", "Month" = "Month"))
monthly_profit$Profit <- monthly_profit$Amt_Repay - monthly_profit$Amt_Spend
monthly_profit$Profit <- ifelse(monthly_profit$Profit > 0, monthly_profit$Profit * 0.29, 0)
monthly_profit
```

#### Q2(f). TOP 5 PRODUCT TYPES

```{r}
top_5_products <- customer_spend %>% dplyr::group_by(customer_spend$Type) %>% 
                  summarise(Frequency = n()) %>% arrange(desc(Frequency)) %>% head(5)
print(top_5_products)
```

### Q2(g). CITY HAVING MAXIMUM SPEND

```{r}
city_max_spend <- customer_spend %>% dplyr::group_by(customer_spend$City) %>%
                  summarise(Total_Spend = sum(Amt_Spend)) %>% arrange(desc(Total_Spend)) %>%
                  head(1)
print(city_max_spend)
```

### Q2(h). EXPENDITURE ON BASIS OF AGE GROUP 

```{r}
customer_spend$Age_Group <- ifelse(customer_data$Age > 65, "Old(>65)", 
                                  ifelse(customer_data$Age > 50, "Senior(51-65)",
                                         ifelse(customer_data$Age > 30, "Middle Age(31-50)",
                                                ifelse(customer_data$Age >= 18, "Young(18-30)"))))
age_group_spend <- customer_spend %>% dplyr::group_by(Age_Group) %>% 
                   summarise(Total_Spend = sum(Amt_Spend)) %>% arrange(desc(Total_Spend))
print(age_group_spend)
```

### Q2.(i) TOP 10 CUSTOMERS IN TERMS OF REPAYMENT.

```{r}
top_10_repayments <- customer_repay %>% dplyr::group_by(Customer) %>% 
                     summarise(Total_Repayment = sum(Amt_Repay)) %>% 
                     arrange(desc(Total_Repayment)) %>% head(10)
print(top_10_repayments)
```

### Q3. CITYWISE SPEND ON EACH PRODUCT ON YEARLY BASIS.

```{r}
city_analysis <-customer_spend %>% dplyr::group_by(City, Type, lubridate::year(Month)) %>% 
                                   summarise(Spend = sum(Amt_Spend))
city_analysis <- dplyr::rename(city_analysis, "Year" = "lubridate::year(Month)")
city_analysis <- data.frame(city_analysis)
print(head(data.frame(city_analysis), 5))

city_analysis_plot <- ggplot2::ggplot(data = city_analysis) + 
                               aes(x = City, y = Spend, fill = Type) + 
                               geom_bar(stat = "identity") + facet_grid(Year~.)
plot(city_analysis_plot)
city_analysis_plot <- plotly::ggplotly(city_analysis_plot)
city_analysis_plot
```

### Q4(a). MONTHLY COMPARISON OF TOTAL SPENDS CITYWISE.

```{r}
spend_citywise <- customer_spend %>% 
                  dplyr::group_by(lubridate::year(Month),lubridate::month(Month), City) %>%
                  summarise(Spend = sum(Amt_Spend))
spend_citywise <- dplyr::rename(spend_citywise, "Year" = "lubridate::year(Month)",
                                                "Month" = "lubridate::month(Month)")
spend_citywise$Month <- lubridate::month(spend_citywise$Month, label = TRUE)
spend_citywise_plot <- ggplot2::ggplot(data = spend_citywise) + 
                                aes(x = City, y = Spend, fill = Month) + 
                                geom_bar(stat = "identity") + facet_grid(Year~.)
spend_citywise_plot <- plotly::ggplotly(spend_citywise_plot)
spend_citywise_plot
```

### Q4(b). COMPARISON OF YEARLY SPEND ON AIR TICKET.

```{r}
spend_airticket <- customer_spend[customer_spend$Type == "AIR TICKET", ] %>%
                                  dplyr::group_by(lubridate::year(Month)) %>% 
                                  dplyr::summarise(Yearly_Spend = sum(Amt_Spend)) 
spend_airticket <- dplyr::rename(spend_airticket, "Year" = "lubridate::year(Month)")
spend_airticket_plot <- ggplot2::ggplot(data = spend_airticket) + 
                        aes(x = Year, y = Yearly_Spend) + 
                        geom_bar(stat = "identity")
spend_airticket_plot <- plotly::ggplotly(spend_airticket_plot)
spend_airticket_plot
```

### Q4(c). COMPARISON OF MONTHLY SPEND OF FOR EACH PRODUCT.

```{r}
product_spend <- customer_spend %>% 
                 dplyr::group_by(lubridate::year(Month), lubridate::month(Month), Type ) %>%
                 summarise(Spend = sum(Amt_Spend))
product_spend <- dplyr::rename(product_spend, "Year" = "lubridate::year(Month)", 
                                              "Month" = "lubridate::month(Month)")
product_spend$Month <- lubridate::month(product_spend$Month, label = TRUE)
product_spend$Year <- as.factor(product_spend$Year)
product_spend_plot <- ggplot2::ggplot(data = product_spend) + 
                               aes(x = Month, y = Spend, fill = Year) + 
                               geom_bar(stat = "identity", position = "dodge") + 
                               facet_grid(Type~.)
product_spend_plot <- plotly::ggplotly(product_spend_plot)
product_spend_plot
```

### Q5. USER DEFINED FUNCTION FOR ANALYSIS.

```{r}
# CORRECTING A MINOR MISTAKE
customer_repay[customer_repay$Product == "Platimum", "Product"] <- "Platinum"

top_10_cust_repay <- function(product, period){
  
  data <- customer_repay[customer_repay$Product == product, ]
  
  if(period == "year"|period == "Year"|period == "Yearly"|period == "yearly"|period == "YEAR"|period == "YEARLY")
  {
    data_summary <- data %>% dplyr::group_by(Customer, City, lubridate::year(Month)) %>%
                                    summarise(Repayment = sum(Amt_Repay)) %>%
                                    arrange(City, desc(Repayment))
    
    data_summary <- dplyr::rename(data_summary, "Year" = "lubridate::year(Month)")
  } 
  
  else if(period == "month"|period == "monthly"|period == "MONTH"|period == "MONTHLY"|period == "Month"|period == "Monthly")
  {
    data_summary <- data %>% dplyr::group_by(Customer, City, lubridate::month(Month)) %>%
                                    summarise(Repayment = sum(Amt_Repay)) %>%
                                    arrange(City, desc(Repayment))
    
    data_summary <- dplyr::rename(data_summary, "Month" = "lubridate::month(Month)")
  }
  
  View(data_summary)
  
  data_bangalore <- head(data_summary[data_summary$City == "BANGALORE", ], 10)
  data_bombay <- head(data_summary[data_summary$City == "BOMBAY", ], 10)
  data_calcutta <- head(data_summary[data_summary$City == "CALCUTTA", ], 10)
  data_chennai <- head(data_summary[data_summary$City == "CHENNAI", ], 10)
  data_cochin <- head(data_summary[data_summary$City == "COCHIN", ], 10)
  data_delhi <- head(data_summary[data_summary$City == "DELHI", ], 10)
  data_patna <- head(data_summary[data_summary$City == "PATNA", ], 10)
  data_trivandrum <- head(data_summary[data_summary$City == "TRIVANDRUM", ], 10)
  
  final_data <- rbind(data_bangalore, data_bombay, data_calcutta, data_chennai, data_cochin, data_delhi, data_patna, data_trivandrum)
  
  if(period == "year")
  {
    final_data <- final_data %>% dplyr::group_by(Customer, City) %>% summarise %>% arrange(City)
  }
  
  else if(period == "month")
  {
    final_data <- final_data %>% dplyr::group_by(Customer, City) %>% summarise %>% arrange(City)
  }
  
  final_data
}


top_10_cust_repay("Gold", "month")
top_10_cust_repay("Platinum", "year")
```









