```{r}
################################################################################
########################### RETAIL CASE STUDY ##################################
################################################################################
```

```{r}
setwd("C:/Users/shubh/Desktop/Data Science Using R")

customer <- read.csv("Class 7 Data Science Using R/R Retail Case Study/Customer.csv")
head(customer, 2)  

product_cat_info <- read.csv("Class 7 Data Science Using R/R Retail Case Study/prod_cat_info.csv")
head(product_cat_info, 2)

transactions <- read.csv("Class 7 Data Science Using R/R Retail Case Study/Transactions.csv")
head(transactions, 2)
```

```{r}
require(dplyr)
require(ggplot2)
require(plotly)
require(lubridate)
```

### Q1(a). MERGING THE DATASETS BY USING BASE R PACKAGE.

```{r}
customer_final_sub <- merge(x = customer, y = transactions, by.x = "customer_Id", by.y =     
                            "cust_id", all.y = TRUE)

customer_final <- merge(x = customer_final_sub, y = product_cat_info, 
                        by.x = c("prod_cat_code", "prod_subcat_code"),
                        by.y = c("prod_cat_code", "prod_sub_cat_code"),
                        all.x = TRUE)

head(customer_final, 2)
```

### Q1(b). MERGING THE DATASETS BY USING DPLYR PACKAGE.

```{r}
customer_final_sub2 <- dplyr::right_join(x = customer, y = transactions, by = c("customer_Id" = "cust_id"))

customer_final2 <- dplyr::left_join(x = customer_final_sub, y = product_cat_info,
                                   by = c("prod_cat_code"= "prod_cat_code", "prod_subcat_code"= "prod_sub_cat_code"))

head(customer_final, 2)
```

### Q2. CREATING A SUMMARY FOR MERGED DATASETS.

### (a) Getting Column Names Along With Data Types.

```{r}
sapply(customer_final2, class)
```

### (b) Top / Bottom 10 Oservations

```{r}
head(customer_final2, 10)
tail(customer_final2, 10)
```

### (c) Summary for continuous variables

```{r}
dtypes <- sapply(customer_final2, class)
summary(customer_final2[dtypes == "integer" | dtypes == "numerical"])
```

### (d) Frequency Table for Categorical Variables

```{r}
dplyr.summarise.inform = FALSE 

freq_gender <- dplyr::group_by(customer_final2, Gender) 
dplyr::summarise(freq_gender, Frequency = n())

freq_citycode <- dplyr::group_by(customer_final2, city_code)
dplyr::summarise(freq_citycode, Frequency = n())

freq_prodcode <- customer_final2 %>% dplyr::group_by(prod_cat_code, prod_subcat_code)
dplyr::summarise(freq_prodcode, Frequency = n())

freq_prodname <- customer_final2 %>% dplyr::group_by(prod_cat, prod_subcat)
dplyr::summarise(freq_prodname, Frequency = n())

freq_storetype <- dplyr::group_by(customer_final2, Store_type)
dplyr::summarise(freq_storetype, Frequency = n())


```

### Q3. GENERATE HISTOGRAM FOR ALL CONTINUOUS VARIABLES AND 
###     FREQUENCY BARS FOR ALL CATEGORICAL VARIABLES

```{r}
histogram_qty <- ggplot2::ggplot(data = customer_final2) + 
                 aes(x = Qty) + geom_histogram(bins = 30, fill = "skyblue") + 
                 xlab("Quantity") + ylab("Frequency")
plotly::ggplotly(histogram_qty)

histogram_rate <- ggplot2::ggplot(data = customer_final2) + 
                 aes(x = Rate) + geom_histogram(bins = 30, fill = "skyblue") + 
                 xlab("Rate") + ylab("Frequency")
plotly::ggplotly(histogram_rate)

histogram_amount <- ggplot2::ggplot(data = customer_final2) + 
                 aes(x = total_amt) + geom_histogram(bins = 30, fill = "skyblue") + 
                 xlab("Total Amount") + ylab("Frequency")
plotly::ggplotly(histogram_amount)


histogram_tax <- ggplot2::ggplot(data = customer_final2) + 
                 aes(x = Tax) + geom_histogram(bins = 30, fill = "skyblue") + 
                 xlab("Tax") + ylab("Frequency")
plotly::ggplotly(histogram_tax)
```

```{r}
barchart_gender <- ggplot2::ggplot(data = customer_final2) +
                   aes(x = Gender) + geom_bar() +
                   xlab("Gender") + ylab("Frequency") 
plotly::ggplotly(barchart_gender) 

barchart_citycode <- ggplot2::ggplot(data = customer_final2) +
                     aes(x = city_code) + geom_bar() +
                     xlab("City Code") + ylab("Frequency") 
plotly::ggplotly(barchart_citycode) 

barchart_storetype <- ggplot2::ggplot(data = customer_final2) +
                      aes(x = Store_type) + geom_bar() +
                      xlab("Store Type") + ylab("Frequency") 
plotly::ggplotly(barchart_storetype) 

barchart_product <- ggplot2::ggplot(data = customer_final2) +
                    aes(x = prod_cat) + geom_bar() +
                    xlab("Product Category") + ylab("Frequency") 
plotly::ggplotly(barchart_product) 

barchart_subproduct <- ggplot2::ggplot(data = customer_final2) +
                    aes(x = prod_subcat) + geom_bar() +
                    xlab("Product Sub-Category") + ylab("Frequency") 
plotly::ggplotly(barchart_subproduct) 
```

### Q4(a). TIME PERIOD OF AVAILABLE TRANSACTION DATA

```{r}
customer_final2$tran_date <- lubridate::dmy(customer_final2$tran_date)
time_period_days <- max(customer_final2$tran_date) - min(customer_final2$tran_date)
time_period_days

time_period_years <- year(max(customer_final2$tran_date)) - year(min(customer_final2$tran_date))
time_period_years
```

### Q4(b). COUNT OF TRANSACTIONS WITH NEGATIVE AMOUNT ????

```{r}
count(customer_final2[customer_final2$total_amt < 0,]) 
```

### Q5. ANALYZE POPULAR CATEGORIES AMONG FEMALE VS. MALES

```{r}
female_data <- customer_final2[customer_final2$Gender == "F",]
male_data <- customer_final2[customer_final2$Gender == "M",]

female_popular_cat <- female_data %>% group_by(prod_cat) %>% summarise(Frequency = n())
female_popular_cat <- dplyr::arrange(female_popular_cat, desc(Frequency))
female_popular_cat[c(1:3),]

male_popular_cat <- male_data %>% group_by(prod_cat) %>% summarise(Frequency = n())
male_popular_cat <- dplyr::arrange(male_popular_cat, desc(Frequency))
male_popular_cat[c(1:3),]
```

### Q6. CITY CODE WITH MAXIMUM CUSTOMERS ALONG WITH PERCENTAGE OF CUSTOMERS

```{r}
max_cust_city <- customer_final2 %>% dplyr::group_by(city_code) %>%                                  
                 summarise(Count_Of_Cust = n()) %>% arrange(desc(Count_Of_Cust))
print(max_cust_city[1,])
max_cust_city_pct <- (max_cust_city[1,2]/sum(max_cust_city$Count_Of_Cust))*100
print(paste(max_cust_city_pct, "%"))
```

### Q7(a). STORETYPE SELLING MAXIMUM PRODUCTS BY VALUE

```{r}
max_sales_value <- customer_final2[customer_final2$total_amt > 0, ] %>%            
                   dplyr::group_by(Store_type) %>% 
                   summarise(Total_Sales_Value = sum(total_amt)) %>%
                   arrange(desc(Total_Sales_Value))
max_sales_value[1,]
```

### Q7(b). STORETYPE SELLING MAXIMUM PRODUCTS BY QUANTITY

```{r}
max_sales_qty <- customer_final2[customer_final2$Qty > 0, ] %>%            
                   dplyr::group_by(Store_type) %>% 
                   summarise(Total_Sales_Qty = sum(Qty)) %>%
                   arrange(desc(Total_Sales_Qty))
max_sales_qty[1,]
```

### Q8. TOTAL AMOUNT EARNED FROM ELECTRONICS AND CLOTHING CATEGORIES FROM FLAGSHIP STORES

```{r}
elec_clth_flg <- customer_final2[customer_final2$Store_type == "Flagship store" & 
                 (customer_final2$prod_cat == "Electronics" | customer_final2$prod_cat == "Clothing") &
                  customer_final2$total_amt > 0, ]
elec_clth_flg_amt <- sum(elec_clth_flg$total_amt)
print(paste("Amount Earned = ", elec_clth_flg_amt))
```

### Q9. AMOUNT EARNED FROM MALE CUSTOMERS IN ELECTRONICS CATEGORY

```{r}
amt_elec_male <- sum(customer_final2[customer_final2$Gender == "M" & 
                                     customer_final2$prod_cat == "Electronics" &
                                     customer_final2$total_amt > 0, ]$total_amt)
print(paste("Amount Earned = ", amt_elec_male))
```

### Q10. CUSTOMERS WITH 10 UNIQUE TRANSACTIONS

```{r}
unique_transactions <- customer_final2[customer_final2$total_amt > 0, ] %>%
                       dplyr::group_by(customer_Id) %>% 
                       summarise(No_Of_Transactions = n()) %>% 
                       arrange(desc(No_Of_Transactions))
unique_transactions_count <- count(unique_transactions[unique_transactions$No_Of_Transactions > 10, ])
print(paste("No. of customers with more than 10 transactions = ", unique_transactions_count))
```

### Q11(a). TOTAL AMOUNT SPENT FOR ELECTRONICS & BOOKS CATEGORIES (AGE B/W 25-35)

```{r}
customer_final2$DOB <- lubridate::dmy(customer_final2$DOB)
q11_data <- dplyr::group_by(customer_final2, customer_Id, tran_date) %>% arrange(customer_Id, desc(tran_date))
q11_data <- q11_data[, c(1,2,6)]
head(q11_data, 5)
q11_data$age <- as.integer((q11_data$tran_date - q11_data$DOB)/365)
q11_data <- q11_data %>% dplyr::group_by(customer_Id) %>% summarise(max(age))
customer_final2 <- dplyr::left_join(customer_final2, q11_data, by = "customer_Id")
customer_final2 <- dplyr::rename(customer_final2, "age" = "max(age)")

amt_elec_books <- sum(customer_final2[(customer_final2$prod_cat == "Electronics" | 
                                       customer_final2$prod_cat == "Books") & 
                                       customer_final2$total_amt > 0 &
                                      (customer_final2$age >= 25 | customer_final2$age <= 35), ]$total_amt)
print(paste("Amount earned from people aged b/w 25 and 35 in elec. & books catg. is ", amt_elec_books))
```

### Q11(b). AMOUNT SPENT B/W 1-1-2014 & 1-3-2014 BY CUST AGED B/W 25 & 35

```{r}
transaction_date_1114_1314 <- (customer_final2$tran_date >= lubridate::ymd("2014,01,01") & 
                               customer_final2$tran_date <= lubridate::ymd("2014,03,01"))

amt_spt_1114_1314 <- sum(customer_final2[customer_final2$total_amt > 0 &
                                         transaction_date_1114_1314, ]$total_amt)
print(paste("Amount earned from people aged b/w 25 and 35 b/w 1-1-14 & 1-3-14 is ", amt_spt_1114_1314))

```












