---
title: "R VISUALIZATION CASE STUDY - shubhamjainxyz@gmail.com"
author: "Shubham Jain"
output: html_document
---
### IMPORTING DATASET

```{r}
sales_data <- read.csv("Class 7 Data Science Using R/CaseStudy_R_Visualizations/SalesData.csv")
head(sales_data, 2)
```

### IMPORTING PACKAGES 

```{r}
require(dplyr)
require(ggplot2)
require(plotly)
require(reshape2)
require(gridExtra)
```

### Q1. COMPARE SALES BY REGION FOR 2015 AND 2016

```{r}
sales_15_16 <- sales_data %>% dplyr::group_by(Region) %>% 
               summarise(TotalSales2015 = sum(Sales2015), TotalSales2016 = sum(Sales2016))
sales_15_16 <- reshape2::melt(sales_15_16, "Region")
sales_15_16 <- dplyr::rename(sales_15_16, "Year" = "variable", "Sales" = "value")
sales_15_16_plot <- ggplot2::ggplot(data = sales_15_16) + 
                             aes(x = Region, y = Sales, fill = Year ) +
                             geom_bar(stat = "identity", position = "dodge")

sales_15_16_plot <- plotly::ggplotly(sales_15_16_plot)
sales_15_16_plot
```

### Q2. CONTRIBUTING FACTOR TO SALES IN EACH REGION FOR 2016.

```{r}
pie_data <- sales_data %>% dplyr::group_by(Region) %>%
                           summarise(Sales = sum(Sales2016))
pie_data$percentage <- as.integer((pie_data$Sales/sum(pie_data$Sales))*100)
pie_chart <- pie(pie_data$Sales, labels = paste(pie_data$Region, "  ",
                                               (pie_data$percentage), "%"))
pie_chart
```

### Q3. TOTAL SALES OF 2015 AND 2016 W.R.T REGIONS AND TIERS.

```{r}
q3_data <- sales_data %>% dplyr::group_by(Region, Tier) %>% 
                          summarise(TotalSales2015 = sum(Sales2015), TotalSales2016 = sum(Sales2016)) 
q3_data <- reshape2::melt(q3_data, c("Region", "Tier"))
q3_data <- dplyr::rename(q3_data, "Year" = "variable", "Sales" = "value")
q3_plot <- ggplot2::ggplot(data = q3_data) + 
                    aes(x = Tier, y = Sales, fill = Year) + 
                    geom_bar(stat = "identity", position = "dodge") + 
                    facet_grid(.~Region)
q3_plot <- plotly::ggplotly(q3_plot)
q3_plot
```

### Q4. DECLINE(Sales) IN STATE IN 2016 VS. 2015 IN EAST REGION.

```{r}
q4_data <- sales_data[sales_data$Region == "East", ] %>%
           dplyr::group_by(State) %>% 
           summarise(TotalSales2015 = sum(Sales2015), TotalSales2016 = sum(Sales2016))
q4_data <- reshape2::melt(q4_data, "State")
q4_data <- dplyr::rename(q4_data, "Year" = "variable", "Sales" = "value")
q4_plot <- ggplot2::ggplot(data = q4_data) + 
           aes(x = State, y = Sales, fill = Year) + 
           geom_bar(stat = "identity", position = "dodge")
q4_plot <- plotly::ggplotly(q4_plot)
q4_plot

# STATE NY REGISTERED A DECLINE IN SALES IN 2016 COMPARED TO 2015
```

### Q5. IN HIGH TIER WHICH DIVISION SAW A DECLINE IN UNIT SALES IN 2016 VS. 2015.

```{r}
q5_data <- sales_data[sales_data$Tier == "High", ] %>% 
           dplyr::group_by(Division) %>%
           summarise(UnitSales2015 = sum(Units2015), UnitSales2016 = sum(Units2016))
q5_data <- reshape2::melt(q5_data, "Division")
q5_data <- dplyr::rename(q5_data, "Year" = "variable", "UnitSales" = "value")
q5_plot <- ggplot2::ggplot(data = q5_data) + 
           aes(x = Division, y = UnitSales, fill = Year) + 
           geom_bar(stat = "identity", position = "dodge") + 
           theme(axis.text.x = element_text(angle = 90))
q5_plot <- plotly::ggplotly(q5_plot)
q5_plot

# NONE OF THE DIVISION SAW A DECLINE IN UNIT SALES IN 2016 COMPARED TO 2015
```

### Q6. CREATING A NEW COLUMN QTR(QUARTER).

```{r}
sales_data$Qtr <- ifelse(sales_data$Month == "Jan" | 
                           sales_data$Month == "Feb" | 
                            sales_data$Month == "Mar", "Q1", 
                         ifelse(sales_data$Month == "Apr" | 
                                  sales_data$Month == "May" | 
                                   sales_data$Month == "Jun", "Q2",
                                ifelse(sales_data$Month == "Jul" | 
                                         sales_data$Month == "Aug" | 
                                          sales_data$Month == "Sep", "Q3", "Q4")))
head(sales_data, 2)
```

### Q7. COMPARE QUARTER WISE SALES IN 2015 VS 2016.

```{r}
q7_data <- sales_data %>% 
           dplyr::group_by(Qtr) %>% 
           summarise(TotalSales2015 = sum(Sales2015), TotalSales2016 = sum(Sales2016))
q7_data <- reshape2::melt(q7_data, "Qtr")
q7_data <- dplyr::rename(q7_data, "Year" = "variable", "Sales" = "value")

q7_plot <- ggplot2::ggplot(data = q7_data) + 
           aes(x = Qtr, y = Sales, fill = Year) + 
           geom_bar(stat = "identity", position = "dodge")
q7_plot <- plotly::ggplotly(q7_plot)
q7_plot

```

### Q8. COMPOSITION OF QUARTER WISE SALES IN 2016 W.R.T ALL TIERS.

```{r}
par(mfrow = c(2,2))
par(mar=c(1,1,1,1))
q8_data_1 <- sales_data[sales_data$Qtr == "Q1", ] %>% 
             dplyr::group_by(Tier) %>% 
             summarise(Sales = sum(Sales2016))
pie(q8_data_1$Sales, labels = q8_data_1$Tier)
title("Qtr1")

q8_data_2 <- sales_data[sales_data$Qtr == "Q2", ] %>% 
             dplyr::group_by(Tier) %>% 
             summarise(Sales = sum(Sales2016))
pie(q8_data_2$Sales, labels = q8_data_2$Tier)
title("Qtr2")

q8_data_3 <- sales_data[sales_data$Qtr == "Q3", ] %>% 
             dplyr::group_by(Tier) %>% 
             summarise(Sales = sum(Sales2016))
#pie(q8_data_3$Sales, labels = q8_data_3$Tier)
#title("Qtr3")
############################################################################################
###  CANNOT PLOT PIE CHART FOR QTR3 AS SALES FOR OUT TIER IS COMING OUT TO BE NEGATIVE   ###
############################################################################################           
q8_data_4 <- sales_data[sales_data$Qtr == "Q4", ] %>% 
             dplyr::group_by(Tier) %>% 
             summarise(Sales = sum(Sales2016))
pie(q8_data_4$Sales, labels = q8_data_4$Tier)
title("Qtr4")

par(mfrow = c(1,1))
```

